SciPy - some descriptive title here

### 2018-06-02 scipy-1.0/paper.tex
Second round of revisions for PR 29.

SciPy adopted an official Governance Document on August 3, 2017 (see PR\#6953). In summary,
we have a Benevolant Dictator for Life (BDFL) in Pauli Virtanen, and a (currently) 18
member Steering Council chaired by Ralf Gommers that i.e., decides on who gets commit rights.

SciPy adopted an official Code of Conduct on October 24, 2017 (see PR\#7963), drawing
inspiration from the Apache Foundation Code of Conduct, the Contributor Covenant,
the Jupyter Code of Conduct, and the Open Source Guides - Code of Conduct. In short,
we stated five specific guidelines: \emph{be open} (to anyone participating in our community),
\emph{be empathetic and patient} (in resolving conflicts), \emph{be collaborative} (we depend
on each other to build up the tools in the library), \emph{be inquisitive} (identifying issues
early on can be helpful to everyone), and \emph{be careful with wording} (do not harass or exclude).
We outline a broad diversity inclusion statement, and provide
instructions for contacting the three members of our Code of Conduct Committee or an
external representative on the NumFOCUS Board of Directors.

>>>>

SciPy adopted an official Governance Document on August 3,
2017\cite{SciPyProjectGovernance}.
We have a Benevolant Dictator for Life (BDFL), Pauli Virtanen, leading the
project, following a detailed discussion of the governance model with the
community on the mailing list.  In practice, the overruling authority of the BDFL
is anticipated to be used only when the Steering Council cannot agree on a matter.
The BDFL is expected to consider any strong indications that they should step down;
although the BDFL may appoint a successor it is generally expected that the Steering
Council will be consulted on the matter.

The (currently) 18 member Steering Council is chaired by Ralf Gommers and performs a number of
tasks including nominating and voting on new Council Members, and actively
contributing to the progress of the project (could be code review but also
outreach activities, etc.). Generally, 1 year of sustained and substantial
contributions (not restricted to source code contributions) that improve
the project are the prerequiste for nomination of new Council Members. Council
Members do not get special treatment for the vast majority of the day to day
project activities (code submission / review), though it is anticipated that their
experience with the project will serve as helpful guidance in many matters.
Council Members have commit rights to the project, but will typically only
incorporate changes when there are no substantive community objections. The
Chair of the Steering Council is responsible for starting more formal
technical reviews of the direction of the project, ensuring that the
composition of the Council remains current, and communicating / summarizing
any Council activities performed privately to the broader community. We also
describe in some detail how institutional partners may contribute to the
project, but no financial weight from grants or other sources
may be leveraged to circumvent or overrule the technical direction of the
project decided upon by the Steering Committee. The Chair does not have
a fixed term, but is nominated by the Steering Committee and is expected
to yield to substantive claims that stepping down is the appropriate action.

SciPy adopted an official Code of Conduct on October 24, 2017
\cite{SciPyCodeOfConduct}, drawing
inspiration from the Apache Foundation Code of
Conduct\cite{ApacheCodeOfConduct}, the Contributor Covenant
\cite{ContributorConvenant},
the Jupyter Code of Conduct \cite{Jupyter_COC}, and the Open Source Guides -
Code of Conduct\cite{OSG_COC}. In short,
we stated five specific guidelines: \emph{be open} (to anyone participating in our community),
\emph{be empathetic and patient} (in resolving conflicts), \emph{be collaborative} (we depend
on each other to build up the tools in the library), \emph{be inquisitive} (identifying issues
early on can be helpful to everyone), and \emph{be careful with wording} (do not harass or exclude).
We outlined a broad diversity inclusion statement, and provide
instructions for contacting the three members of our Code of Conduct Committee or an
external representative on the NumFOCUS Board of Directors.
